Article Title

### 2020-12-22 paper/aa-package/paper.tex
abstract

   \title{Time delay estimation in non-resolved lensed quasars}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {
   	Early universe (EU) measurements and late universe (LU) observations have resulted in a tension on the estimated value of the Hubble parameter $H_0$. Time-delay cosmography offers an alternative method to measure $H_0$. In this context, the H0LiCoW collaboration has reported a $2.4\%$ measurement of $H_0$ compatible with LU observations, increasing the tension at the $5.3 \sigma$ level. Whereas, TDCOSMO+SLACS has reported a $5\%$ measurement of $H_0$ in agreement with both EU and LU estimates, showing the need to collect more data in order to reduce the error in the $H_0$ estimation.
   	}
  % aims heading (mandatory)
   { 
   	The fractional error on $H_0$ is directly related to the error in the measurement of relative time delays and it linearly decreases with the number of lensed systems analysed. Therefore, in order to reduce it, more lensed systems should be analysed and, possibly, with a regular and long-term monitoring of the lensed source, of the order of years. This cannot be achieved with big telescopes, due to the huge amount of observational requests they have to fulfill. On the other hand, small/medium-sized telescopes are present in a much larger number and are often characterized by more versatile observational programs. However, the limited resolution capabilities of such instruments and their often not privileged geographical location prevent them from providing well-separated images of the same lensed source. 
   	\\
   	In this work, we present a novel approach to estimate the time-delay in unresolved lensed quasar systems. Our method is further motivated by recent developments in discovering more unresolved strongly-lensed QSO systems.
	}
  % methods heading (mandatory)
   {Our method uses ...}
  % results heading (mandatory)
   {...}
  % conclusions heading (optional), leave it empty if necessary 
   {}

>>>>

   \title{Time delay estimation in unresolved lensed quasars}

@@

  \abstract
  % context heading (optional)
  % {} leave it empty if necessary  
   {
   	Early universe (EU) measurements and late universe (LU) observations have resulted in a tension on the estimated value of the Hubble parameter $H_0$. Time-delay cosmography offers an alternative method to measure $H_0$. In this respect, the H0LiCoW collaboration has reported a $2.4\%$ measurement of $H_0$ compatible with LU observations, increasing the tension at the $5.3 \sigma$ level. Whereas, TDCOSMO+SLACS has reported a $5\%$ measurement of $H_0$ in agreement with both EU and LU estimates, showing the need to collect more data in order to reduce the error in the $H_0$ estimation.
   	}
  % aims heading (mandatory)
   { 
   	In time-delay cosmography, the fractional error on $H_0$ is directly related to the error of relative time delays measurements and it linearly decreases with the number of lensed systems considered. Therefore, in order to reduce it, more lensed systems should be analysed and, possibly, with a regular and long-term monitoring, of the order of years. This cannot be achieved with big telescopes, due to the huge amount of observational requests they have to fulfill. On the other hand, small/medium-sized telescopes are present in a much larger number and are often characterized by more versatile observational programs. However, the limited resolution capabilities of such instruments and their often not privileged geographical location prevent them from providing well-separated images of the same lensed source. 
   	\\
   	In this work, we present a novel approach to estimate the time-delay in unresolved lensed quasar systems. Our proposal is further motivated by recent developments in discovering more unresolved strongly-lensed QSO systems.
	}
  % methods heading (mandatory)
   {Our method uses ...}
  % results heading (mandatory)
   {...}
  % conclusions heading (optional), leave it empty if necessary 
   {}

### 2020-12-22 paper/paper.tex
abstract

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{Article Title} % Article title
\author{%
\textsc{John Smith}\thanks{A thank you or further information} \\[1ex] % Your name
\normalsize University of California \\ % Your institution
\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent The recent tensions on the measured value of the Hubble parameter $H_0$ between cosmic microwave background radiation and astrophysical observations have triggered the need of new methods for its determination. In view of this, an effort has been done by the H0LiCoW collaboration to use the gravitational lensing of quasars as a probe for $H_0$ through the measurement of the time delay between the multiple images of the lensed quasar. Measurements of the time delay require a long term monitoring of lensed quasars, of the order of years. Since big telescopes have to deal with many observational requests, it is difficult to have a regular monitoring campaign over the years, therefore this task can be achieved more easily by small/medium sized telescopes. However, the number of lensed quasars with multiple images that can be angularly resolved by these telescopes drops drastically. Here we present a method to deal with \textbf{non fully resolved} lensed quasars. This method has also the advantage of being less dependent on the microlensing effect of the lens galaxy.
\end{abstract}
}

>>>>

\pretitle{\begin{center}\Huge\bfseries} % Article title formatting
\posttitle{\end{center}} % Article title closing formatting
\title{Article Title} % Article title
\author{%
\textsc{John Smith}\thanks{A thank you or further information} \\[1ex] % Your name
\normalsize University of California \\ % Your institution
\normalsize \href{mailto:john@smith.com}{john@smith.com} % Your email address
%\and % Uncomment if 2 authors are required, duplicate these 4 lines if more
%\textsc{Jane Smith}\thanks{Corresponding author} \\[1ex] % Second author's name
%\normalsize University of Utah \\ % Second author's institution
%\normalsize \href{mailto:jane@smith.com}{jane@smith.com} % Second author's email address
}
\date{\today} % Leave empty to omit a date
\renewcommand{\maketitlehookd}{%
\begin{abstract}
\noindent The recent tensions on the measured value of the Hubble parameter $H_0$ between cosmic microwave background radiation and astrophysical observations have triggered the need of new methods for its determination. In this respect, an effort has been done by the H0LiCoW collaboration to use the gravitational lensing of quasars as a probe for $H_0$ through the measurement of the time delay between the multiple images of the lensed quasar. Measurements of the time delay require a long term monitoring of lensed quasars, of the order of years. Since big telescopes have to deal with many observational requests, it is difficult to have a regular monitoring campaign over the years, therefore this task can be achieved more easily by small/medium sized telescopes. However, the number of lensed quasars with multiple images that can be angularly resolved by these telescopes drops drastically. Here we present a method to deal with \textbf{non fully resolved} lensed quasars. This method has also the advantage of being less dependent on the microlensing effect of the lens galaxy.
\end{abstract}
}
